% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}
% CV Info (to be customized).
\newcommand{\CVAuthor}{Bjørn Mathisen}
\newcommand{\CVTitle}{Bjørn Mathisens Resume}
\newcommand{\CVNote}{CV compiled on {\today} for the Construction/Carpenter position}
\newcommand{\CVNote}{CV compiled on {\today} for the Construction/Carpenter position}
\newcommand{\CVWebpage}{https://bjornmathisen.com/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={construction, carpentry, maintenance, apprentice},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://goo.gl/maps/PwzyUhnuM922} %shortened link to home address
{265 Melody Lane, Carpentersville, Illinois 60110, USA}
\par
\href{mailto:contact@bjornmathisen.com}
{contact@bjornmathisen.com}
\,\SubBulletSymbol\,
+1\,(224)\,622-8543
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{Bjørn Mathisen}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.principiacollege.edu/}
{\textbf{Principia College}},
Elsah, Illinois
\hfill
\DatestampYMD{2014}{8}{15} --
\DatestampYMD{2018}{12}{12}

\Gap
\BulletItem
B.S. in
\href{http://www.principiacollege.edu/computer-science}
{Computer Science}
\begin{Detail}
\SubBulletItem
Highlighted Courses: Software Architecture, Computer Hardware Architecture, Software Engineering 
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://zerma.com/en}
{\textbf{Zerma}},
Northbrook, Illinois
\hfill \DatestampYMD{2019}{01}{01} --
\DatestampYMD{2019}{06}{28}

\Gap
\BulletItem
Field Engineer

\begin{Detail}
\SubBulletItem
Fascilitated the installation of large industrial grade machinery such as grinders, granulators, and shredders. Delt with customers and plant managers to fascilitate the installation. 
\SubBulletItem
Maintained an inventory of knives, motors and other maintenance items as well as handled the shipping and handling of machinery and parts.
\end{Detail}
\BulletItem
General IT
\begin{Detail}
\SubBulletItem
Created an Access Database linked with Excel from 15 different data sources using a Python web crawler. 
Created an email automated email campaign with over 12 thousand contacts using a custom built in house systems.
\SubBulletItem
Performed maintenance on inventory management computers and sped up operating speeds by eighty percent.
\end{Detail}

%%%%%%%%%%%%%%%%%%

\href{http://www.mccdistrict.org/rccms/}
{\textbf{
McHenry County Conservation District}},
Mchenry, Illinois
\hfill \DatestampYMD{2014}{05}{20} --
\DatestampYMD{2018}{08}{05}

\Gap
\BulletItem
Season Maintenance Construction Worker
\begin{Detail}
\SubBulletItem
Performed maintenance and construction for a park district with over 100 properties. Did demos of buildings and fascilitated the construction and completion of projects with a team of two. 
\SubBulletItem
Framed Windos, poured concretee, built full additions to existing buildings, basic eletrical work and did door installation. Performed any task requested through a work order form and performed general construction for the department. 
\end{Detail}

%%%%%%%%%%%%%%%%%%

{\textbf{Custom Carpentry}},
Carpentersville, Illinois
\hfill
\DatestampYMD{2010}{05}{12} --
\DatestampYMD{2013}{08}{08}

\Gap
\BulletItem
Laborer 

\begin{Detail}
\SubBulletItem
Basic laborer and construction apprentice, carried cinder blocks, demos buildings, shingled roofs. 
\SubBulletItem
Carried heavy loads.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Eagle Scout,
Earned in Spring of 2012,
Boy Scouts of America
\hfill
\DatestampY{2008} --
\DatestampY{2012}
\begin{Detail}
\Item
Attained the rank of Eagle, the highest and most prestigious of all the ranks in Boy Scouts.
\end{Detail}

\Gap
\BulletItem
\href{https://www.toastmasters.org/Education/Communication-Track}{Competent Communicator,
Toastmasters International}
\hfill
\DatestampYMD{2005}{05}{15}
\begin{Detail}
\Item
For delivering 10 speeches and satisfying the requirements for the Competent Communicator Award. 
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL CERTIFICATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
%{Professional Affiliations\newline
%\& Activities}
%{Professional Affiliations \& Activities}
%{PDF:ProfessionalAffiliationsActivities}

%\Entry
%\href{http://www.example.com/my-society}
%{\textbf{Joint Society of Earth Scientists and Global Think Tank on Climate Resiliency}},
%\newline
%North Attleborough, Massachusetts, USA

%\Gap
%\BulletItem
%Member
%\hfill
%\DatestampY{2009} --
%Present

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
\href{http://www.example.com/my-club}
{\textbf{Astronomy Club}},
Principia College

\Gap
\BulletItem
President
\hfill
\DatestampYMD{2015}{01}{01} --
\DatestampYMD{2018}{12}{12}
\begin{Detail}
\SubBulletItem
Created and advertised activities for students campus wide, organized campus presentations with Dr. Laurance Doyle of NASA SETI program.

\Entry
\Gap
\href{https://www.principiasolarcar.com/}
{\textbf{Solar Car}},
Principia College

\BulletItem
Member
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Native language.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
Framing,
Drywall Install,
Basic Eletrical, 
Concretre Pouring and Install,
Blueprint Reading, 

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Digital photography,
Hiking and Camping.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Dr. Tom Fuller}
\newline
Professor of Computer Science and Head of the Computer Science Dept.
\newline
Principia College
\newline
1 Maybeck Place, Elsah, Illinois 62028, USA
\newline
\href{mailto:tom.fuller@principia.edu}
{tom.fuller@principia.edu}

\end{Body}
\end{document}
