% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}
% CV Info (to be customized).
\newcommand{\CVAuthor}{Bjørn Mathisen}
\newcommand{\CVTitle}{Bjørn Mathisens Resume}
<<<<<<< HEAD
\newcommand{\CVNote}{CV compiled on {\today} for the Software Developer Position}
=======
\newcommand{\CVNote}{CV compiled on {\today} for Software Developer Position }
>>>>>>> 5bbf8cad970fb8cb75fac158110d360a2a4f5f7a
\newcommand{\CVWebpage}{https://bjornmathisen.com/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={Resume, Software Developer, Programmer, Entry Level, IT},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://goo.gl/maps/PwzyUhnuM922} %shortened link to home address
{265 Melody Lane, Carpentersville, Illinois 60110, USA}
\par
\href{mailto:contact@bjornmathisen.com}
{contact@bjornmathisen.com}
\,\SubBulletSymbol\,
+1\,(224)\,622-8543
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{Bjørn Mathisen}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.principiacollege.edu/}
{\textbf{Principia College}},
Elsah, Illinois
\hfill
\DatestampYMD{2014}{8}{15} --
\DatestampYMD{2018}{12}{12}

\Gap
\BulletItem
B.S. in
\href{http://www.principiacollege.edu/computer-science}
{Computer Science}
\begin{Detail}
\SubBulletItem
Highlighted Courses: Software Architecture, Computer Hardware Architecture, Software Engineering 
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://zerma.com/en}
{\textbf{Zerma}},
Northbrook, Illinois
\hfill \DatestampYMD{2019}{01}{01} --
\DatestampYMD{2019}{04}{13}

\Gap
\BulletItem
Field Engineer

\begin{Detail}
\SubBulletItem
Handled the installation of granulators and shredders, weighing anywhere from three hundred pounds to twentyfive tons at factories around the United States. 
\SubBulletItem
Maintained an inventory of knives, motors and other maintenance items for shredders, worked with shipping and handling to maintain consistency of records. 
\end{Detail}
\BulletItem
General IT
\begin{Detail}
\SubBulletItem
Created an Access Database linked with Excel from 15 different data sources using a Python web crawler. 
Created an email automated email campaign with over 12 thousand contacts using in house systems.
\SubBulletItem
Performed maintenance on inventory management computers and sped up operating speeds by eighty percent.
\end{Detail}

%%%%%%%%%%%%%%%%%%

\href{http://www.mccdistrict.org/rccms/}
{\textbf{
McHenry County Conservation District}},
Mchenry, Illinois
\hfill \DatestampYMD{2014}{05}{20} --
\DatestampYMD{2018}{08}{05}

\Gap
\BulletItem
Season Maintenance Construction Worker
\begin{Detail}
\SubBulletItem
Worked with a crew of two individuals who operated out of a shop to maintain over forty different parks, buildings and other sites. Duties includes construction work, pouring concrete, building structural maintenance and electrical work.
\end{Detail}

%%%%%%%%%%%%%%%%%%

\href{http://www.mccdistrict.org/rccms/}
{\textbf{Observatory Manager \& Engineering TA}},
Elsah, Illinois
\hfill
\DatestampYMD{2015}{01}{12} --
\DatestampYMD{2018}{12}{12}

\Gap
\BulletItem
Observatory Manager

\begin{Detail}
\SubBulletItem
Organized and trained over eight student operators; maintained the observatory schedule and organized public campus-wide events on a weekly basis.
\SubBulletItem
Updated training manuals and facilitated the upgrade from DOS to EXP for the telescope control system.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Eagle Scout,
Earned in Spring of 2012,
Boy Scouts of America
\hfill
\DatestampY{2008} --
\DatestampY{2012}
\begin{Detail}
\Item
Attained the rank of Eagle, the highest and most prestigious of all the ranks in Boy Scouts.
\end{Detail}

\Gap
\BulletItem
\href{https://www.toastmasters.org/Education/Communication-Track}{Competent Communicator,
Toastmasters International}
\hfill
\DatestampYMD{2005}{05}{15}
\begin{Detail}
\Item
For delivering 10 speeches and satisfying the requirements for the Competent Communicator Award. 
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL CERTIFICATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
%{Professional Affiliations\newline
%\& Activities}
%{Professional Affiliations \& Activities}
%{PDF:ProfessionalAffiliationsActivities}

%\Entry
%\href{http://www.example.com/my-society}
%{\textbf{Joint Society of Earth Scientists and Global Think Tank on Climate Resiliency}},
%\newline
%North Attleborough, Massachusetts, USA

%\Gap
%\BulletItem
%Member
%\hfill
%\DatestampY{2009} --
%Present

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
\href{http://www.example.com/my-club}
{\textbf{Astronomy Club}},
Principia College

\Gap
\BulletItem
President
\hfill
\DatestampYMD{2015}{01}{01} --
\DatestampYMD{2018}{12}{12}
\begin{Detail}
\SubBulletItem
Created and advertised activities for students campus wide, organized campus presentations with Dr. Laurance Doyle of NASA SETI program.

\Entry
\Gap
\href{https://www.principiasolarcar.com/}
{\textbf{Solar Car}},
Principia College

\BulletItem
Member
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Native language.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
{\TeX},
C++,
C\#,
.Net,
Python,
Java,
C,
SQL, MySQL
Scrum,
Agile Development,
Unit Testing/Automated Testing,
Visual Studio/Eclipse/VI,
Linux, Windows
Adobe Photoshop,
Microsoft Word,
Microsoft Excel,
Microsoft PowerPoint.

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Digital photography,
Hiking and Camping.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Dr. Tom Fuller}
\newline
Professor of Computer Science and Head of the Computer Science Dept.
\newline
Principia College
\newline
1 Maybeck Place, Elsah, Illinois 62028, USA
\newline
\href{mailto:tom.fuller@principia.edu}
{tom.fuller@principia.edu}

\end{Body}
\end{document}
