% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}
% CV Info (to be customized).
\newcommand{\CVAuthor}{Bjørn Mathisen}
\newcommand{\CVTitle}{Bjørn Mathisens Resume}
\newcommand{\CVNote}{CV compiled on {\today} for the Software Developer Position}
\newcommand{\CVWebpage}{https://bjornmathisen.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={Resume, Software Developer, Programmer, Entry Level, IT},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://goo.gl/maps/gpk9cV4DUPH9WCLn6} %shortened link to home address
{1511 Laurel, St Paul, Minnesota, 55104}
\par
\href{mailto:contact@bjornmathisen.com}
{contact@bjornmathisen.com}
\,\SubBulletSymbol\,
+1\,(224)\,622-8543
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{Bjørn Mathisen}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.principiacollege.edu/}
{\textbf{Principia College}},
Elsah, Illinois
\hfill
\DatestampYMD{2014}{8}{15} --
\DatestampYMD{2018}{12}{12}

\Gap
\BulletItem
B.S. in
\href{http://www.principiacollege.edu/computer-science}
{Computer Science}
\begin{Detail}
\SubBulletItem
Highlighted Courses: Programming Languages, Data Structures, Database Management Systems, Object-Oriented Programming, Hardware Architecture, Software Engineering, WebDev, Operating Systems, Compilers\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://zerma.com/en}
{\textbf{Zerma}},
Northbrook, Illinois
\hfill \DatestampYMD{2019}{01}{01} --
\DatestampYMD{2019}{06}{28}

\Gap
\BulletItem
Field Engineer - Contract

\begin{Detail}
\SubBulletItem
Traveled to various Central and East coast States maintaining strict industry standards for the installation of granulators, shredders and injection molding machines (industrial factory equipment) this included the physical installation and wiring of the control panels. 
\SubBulletItem
Gained the ability to follow complex wiring diagrams used to debug problems in the operation of the machine. 
\end{Detail}
\Gap
\BulletItem
General IT - Contract
\begin{Detail}
\SubBulletItem
Wrote a python web crawler using lxml requests that scrapped information together for an ad email campaign with 12 thousand contacts generated from website visits. Used this data to create a relational database of customers accessible from a Access.  Performed maintenance on inventory management computers and sped up operating speeds by eighty percent.
\Gap
\end{Detail}

%%%%%%%%%%%%%%%%%%

\href{http://www.mccdistrict.org/rccms/}
{\textbf{
McHenry County Conservation District}},
Mchenry, Illinois
\hfill \DatestampYMD{2014}{05}{20} --
\DatestampYMD{2018}{08}{05}

\Gap
\BulletItem
Maintenance Construction Worker - Seasonal 
\begin{Detail}
\SubBulletItem
Worked with a crew to maintain over eighty different parks, buildings and other sites. Duties includes construction work such as framing, pouring concrete, roofing, building structural maintenance and electrical work.
\Gap
\end{Detail}

%%%%%%%%%%%%%%%%%%

\href{http://www.mccdistrict.org/rccms/}
{\textbf{Observatory Manager \& Engineering TA}},
Elsah, Illinois
\hfill
\DatestampYMD{2015}{01}{12} --
\DatestampYMD{2018}{12}{12}

\Gap
\BulletItem
Observatory Manager

\begin{Detail}
\SubBulletItem
Organized and trained twelve student operators; maintained the observatory schedule and organized public campus-wide events on a weekly basis.
\SubBulletItem
Wrote the training manuals and facilitated the upgrade from Windows DOS to Windows XP for the telescope control system.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Eagle Scout,
Earned in Spring of 2012,
Boy Scouts of America
\hfill
\DatestampY{2008} --
\DatestampY{2012}
\begin{Detail}
\Item
Attained the rank of Eagle, the highest and most prestigious of the ranks in Boy Scouts.
\end{Detail}

\Gap
\BulletItem
\href{https://www.toastmasters.org/Education/Communication-Track}{Communicator Award,
Toastmasters International}
\hfill
\DatestampYMD{2005}{05}{15}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL CERTIFICATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
%{Professional Affiliations\newline
%\& Activities}
%{Professional Affiliations \& Activities}
%{PDF:ProfessionalAffiliationsActivities}

%\Entry
%\href{http://www.example.com/my-society}
%{\textbf{Joint Society of Earth Scientists and Global Think Tank on Climate Resiliency}},
%\newline
%North Attleborough, Massachusetts, USA

%\Gap
%\BulletItem
%Member
%\hfill
%\DatestampY{2009} --
%Present

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
\href{http://www.example.com/my-club}
{\textbf{Astronomy Club}},
Principia College

\Gap
\BulletItem
President
\hfill
\DatestampYMD{2015}{01}{01} --
\DatestampYMD{2018}{12}{12}
\begin{Detail}
\SubBulletItem
Created and advertised activities for students campus wide, organized campus presentations with Dr. Laurance Doyle of NASA SETI program.

\Entry
\Gap
\href{https://www.principiasolarcar.com/}
{\textbf{Solar Car}},
Principia College

\BulletItem
Member
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Native language.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
\BulletItem Primary Languages
\SubBulletItem
C++,
C\#,
.Net,
Python,
C,
SQL, MySQL
Scrum
\Gap
\BulletItem Familiar With
\SubBulletItem
HTML, CSS,
Agile Development,1
Java,
Unit Testing/Automated Testing,
Visual Studio/Eclipse/VI,
Linux, Windows,
Adobe Photoshop,
Microsoft Word,
Microsoft Excel,
Microsoft PowerPoint,
strong communication skills.

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Digital photography,
Hiking and Camping.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Dr. Tom Fuller}
\newline
Professor of Computer Science and Head of the Computer Science Dept.
\newline
Principia College
\newline
1 Maybeck Place, Elsah, Illinois 62028, USA
\newline
\href{mailto:tom.fuller@principia.edu}
{tom.fuller@principia.edu}


\BulletItem
\textbf{Martina Carter}
\newline
Contracted to perform website installation and maintenance. 
\newline
Greater Chicago Area, IL
\newline
{Phone: 847-912-7994}

\end{Body}
\end{document}
